\documentclass[a4paper,12pt]{article}
\usepackage{amsmath}


\begin{document}



\textbf{ \\ Azeem Sarwar \\ Bochumer Str. 32 \\ Nordhausen, Germany RWE Supply \& Trading \\ Human Resources \\ Essen, Germany}
\date{\today}

\textbf{Dear Hiring Team,}

\section{About Me}

I am a highly motivated Full-Stack Developer with over 4 years of experience in designing and building scalable web and mobile applications. My technical expertise includes proficiency in \textbf{React}, \textbf{TypeScript}, and backend technologies like \textbf{Node.js} and \textbf{Express}. I have a strong foundation in \textbf{microservices architecture} and \textbf{event-driven systems}, and have consistently delivered production-quality code while focusing on testing, monitoring, and documentation. I have worked in agile environments, collaborating with cross-functional teams to create innovative solutions that enhance user experiences and support business objectives.

\section{Why RWE}

The IT Developer Graduate Programme at RWE Supply \& Trading caught my attention due to its unique rotational structure, offering the opportunity to work across different functions such as application development, embedded IT for commercial business, and enterprise integration. I am particularly drawn to RWE’s commitment to driving efficiency and innovation within the energy sector, as these are values that I hold in high regard. The chance to rotate through international locations, including London, Singapore, and the USA, further enhances the appeal of this programme, providing a global perspective on IT solutions in the energy industry. I am eager to contribute to RWE's mission and to deepen my understanding of the energy trading landscape through hands-on experience in various IT functions.

\section{Why Me}

I believe my combination of technical expertise, adaptability, and enthusiasm for continuous learning makes me an excellent fit for this programme. My passion for IT development and working in a \textbf{DevOps} environment aligns perfectly with RWE’s goals of fostering innovation through agile practices. My ability to quickly learn and adapt to new challenges, coupled with my analytical mindset and problem-solving skills, will enable me to contribute meaningfully to your team. I am excited by the opportunity to work alongside experts in the field, learn from their experiences, and grow within RWE’s dynamic and supportive environment.
\\
Thank you for considering my application. I look forward to the possibility of discussing how my skills and experiences align with the objectives of the IT Developer Graduate Programme. Please find my CV attached for further details.
\\
\textbf{Sincerely,}



\end{document}
