
%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} 
\usepackage{multicol}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}  


\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth}
    \vspace{-\baselineskip} % Required for vertically aligning minipages

    { \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{Azeem Sarwar}}}} % First name

    \vspace{6pt}

    {\Large Software $\sim$ Engineer} % Career or current job title
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth} % 20% of the page width for the first row of icons
    \vspace{-\baselineskip} % Required for vertically aligning mini pages

    % The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
    \icon{Globe}{11}{\href{https://www.azeemsarwar.de}{portfolio.com}}\\
    \icon{Phone}{11}{\href{tel://004915224214567}{015224214567}}\\
    \icon{MapMarker}{11}Nordhausen,Germany\\

\end{minipage}
\begin{minipage}[t]{0.27\textwidth} % 27% of the page width for the second row of icons
    \vspace{-\baselineskip} % Required for vertically aligning mini pages

    \icon{Envelope}{11}{\href{mailto:azeemsarwarr1@gmail.com}{azeemsarwarr1@gmail.com}}\\
    \icon{Github}{11}{\href{https://github.com/uma-dev}{github.com/azeem-sarwar}}\\
    \icon{LinkedinSquare}{11}{\href{https://www.linkedin.com/in/azeem-sarwarr}{/in/azeem-sarwarr}}\\

\end{minipage}


%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth}
    \cvsect{Summary}
    \vspace{-1pt}
    Highly motivated Full Stack Developer and IoT Engineer with extensive experience in developing responsive web and mobile applications. Skilled in optimizing performance, ensuring scalability, and implementing modern technologies such as React Native, Node.js, AWS, and Firebase. Proven success in reducing application load times by 30\% and improving code quality through efficient practices.
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.465\textwidth}
    \cvsect{Skills}
    \vspace{0.5pt}

    \begin{minipage}[t]{1\textwidth}
        \textbf{Languages:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{1\textwidth}
        JavaScript, Typescripts, Python, PHP, C++, Java, c\# \end{minipage}


    \begin{minipage}[t]{1\textwidth}
        \textbf{Frontend:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{1\textwidth}
        React Native, React.js, Vue.js,Tailwind CSS, Bootstrap CSS, shopify. \end{minipage}

    \begin{minipage}[t]{1\textwidth}
        \textbf{Backend:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{1\textwidth}
        Express.js, Node.js, NestJs, AWS, MongoDB.
    \end{minipage}

    \begin{minipage}[t]{1\textwidth}
        \textbf{Databases:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{1\textwidth}
        SQL, firestore, Firebase DB, MongoDB.
    \end{minipage}
    \begin{minipage}[t]{1\textwidth}
        \textbf{Cloud Tech:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{1\textwidth}
        Aws (Ec2, Amplify, S3, Route53, IAM, Cognito, Aws Iot), kubernetes, docker, Digital Ocean, Firebase
    \end{minipage}
\end{minipage}


%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
\cvsect{Projects}
\begin{entrylist}
    \entry
    {MERN STACK}
    {Postspace}
    {\href{https://postspace.jp/}{postspace.jp}}
    {It is a file-sharing service designed to securely transfer files using email. By adopting end-to-end encryption (E2EE), we prevent data leaks from cyber attacks and accidental forwarding. You can use it as an alternative to email attachments to securely exchange confidential documents and personal information. It integrates Stripe for payments and AWS EC2 for cloud hosting.}
    \entry
    {MERN STACK}
    {Moresty}
    {}
    {A comprehensive salon management system with a mobile app for booking appointments, managing services, and integrating payments through Stripe. It allows salon owners to manage bookings and payments efficiently.}
    \entry
    {MERN STACK}
    {Safar}
    {}
    {A hostel and hotel booking app with a property listing interface, availability checking, and admin dashboard for managing bookings. It features real-time updates and payment processing.}
    \entry
    {MERN STACK}
    {File-Sharing Mobile App}
    {}
    {A secure mobile app for video sharing, offering file storage, user authentication with Firebase, and payments for content creators. The app ensures ease of file uploads and secure sharing.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Education}
\begin{entrylist}
    \entry
    {10/2024 - curr.}
    {Master Computer Engineering (IoT) }
    {Nordhausen University of applied sciences.}
    {Pursuing a Master's in Internet of Things (IoT), focusing on the development of smart devices, sensor networks, cloud-based systems, and data analytics for innovative IoT applications.}
    \entry
    {10/2018 - 06/2024}
    {Bachelors in Software engineering}
    {Pir Mehar Ali Shah Arid Agriculture Rawalpindi}
    {Graduated with a Bachelor's degree in Software Engineering from Arid Agriculture University, Rawalpindi, with a CGPA of 1.1 / 5.0, specializing in Software engineering.}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Experience}
\begin{entrylist}
    \entry
    {03/22-09/24}
    {Full-Stack developer}
    {Mid-Chain technologies}
    {\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item {Developed and implemented responsive web applications using React.js, Next.js, and modern UI libraries such as Material UI and Tailwind CSS.}
            \item {Developed secure and scalable backend systems using Node.js, Express.js, and Next.js API routes to ensure seamless functionality.}
            \item {Managed and optimized MongoDB, Firebase, and DynamoDB databases, improving query efficiency by 20\%.}
            \item {Developed and deployed cloud-native applications on AWS services using Lambda, API Gateway, S3, and Cognito for scalability and performance.}
            \item {Deployed mobile applications using React Native, including features such as push notifications, real-time chat, and payment gateways such as Stripe.}
            \item {Improved code quality through extensive unit and integration testing using tools such as Jest and Postman.}

            \item {Reduced application load times by 30\% through code optimization and refactoring of backend services.}

        \end{itemize}
    }
    \entry
    {6/22-10/22}
    {Mobile Application Intern}
    {AF-Suqure}
    {\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item {Developed cross-platform mobile applications using React Native that ensured high performance and responsiveness.}

            \item {Integrated third-party APIs like Google Maps API and Firebase to extend the apps’ functionalities.}

            \item {Implemented push notifications and real-time chat features for seamless user interaction.}

            \item {Participated in the entire app development cycle, from conception to deployment, and contributed to the team’s goals.}

            \item {Performed unit testing and debugging to ensure the quality of the applications and reduce crash rate by 15\%.}

            \item {Delivered apps that improved customer satisfaction and retention and received positive feedback for usability.}

        \end{itemize}
    }

\end{entrylist}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Languages}
\vspace{-6pt}

\hspace{26mm} \textbf{English} - Professional, \textbf{ German} - basic, \textbf{ Urdu} - Mother tounge

%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Hobbies}
\vspace{-6pt}

\hspace{26mm} \textbf{Multiplayer games} , \textbf{ Cirket} , \textbf{ Fitness, Traveling}

%----------------------------------------------------------------------------------------

\end{document}
