%----------- EXPERIENCE -----------

\section{Experience}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
{Mid-Chain Technologies}{Hybrid}
{Frontend Engineer}{Jul 2022 \textbf{--} Present, Full-time}
\resumeItemListStart
\resumeItem{Designed and developed responsive, accessible user interfaces using \textbf{React.js, React Native}, \textbf{TypeScript}, and \textbf{Storybook}, adhering to modern front-end development practices.}
\resumeItem{Integrated and optimized \textbf{RESTful APIs}, ensuring seamless communication between front-end and back-end systems.}
\resumeItem{Implemented and maintained \textbf{automated testing frameworks} such as \textbf{Jest}, \textbf{React Testing Library}, and \textbf{Cypress} to ensure robust and reliable codebases.}
\resumeItem{Enhanced application performance, reducing page load times by 30\% and improving cross-browser compatibility and responsiveness.}
\resumeItem{Collaborated with Agile teams, including product managers, UX designers, and backend developers, to deliver intuitive and scalable solutions.}
\resumeItem{Utilized \textbf{Docker} and \textbf{Kubernetes} to manage and deploy applications in secure cloud environments.}
\resumeItem{Participated in Agile workflows, contributing to code reviews, pair-programming sessions, and iterative feature development.}
\resumeItemListEnd

\resumeSubheading
{System Pvt. Limited}{Pakistan}
{Full-Stack Developer}{Feb 2021 \textbf{--} Jun 2022, Full-time}
\resumeItemListStart
\resumeItem{Developed responsive web applications using \textbf{React.js}, \textbf{Node.js}, and \textbf{TypeScript}, with a focus on user-friendly and accessible designs.}
\resumeItem{Integrated APIs and backend systems, ensuring seamless data flow and enhanced user interactions.}
\resumeItem{Managed \textbf{Firebase} and \textbf{MongoDB} databases, improving scalability and reducing query times by 20\%.}
\resumeItem{Collaborated in Agile sprints to deliver key features, improving user satisfaction by 25\% through iterative design and development.}
\resumeItem{Implemented \textbf{responsive design principles}, optimizing applications for various devices and platforms.}
\resumeItemListEnd

\resumeSubheading
{Freelance (Willder-Inc Japanese company)}{Remote}
{Front-End Developer}{Oct 2019 \textbf{--} Jan 2021, Full-time}
\resumeItemListStart
\resumeItem{Developed interactive and responsive web applications using \textbf{React.js} and \textbf{Next.js}, tailored to meet client-specific needs.}
\resumeItem{Collaborated with clients to gather requirements, ensuring timely delivery of high-quality, scalable solutions.}
\resumeItem{Optimized designs for cross-browser compatibility and accessibility, enhancing the overall user experience.}
\resumeItem{Built reusable and maintainable components, reducing development time for future projects.}
\resumeItemListEnd

\resumeSubheading
{AFSquare}{Remote}
{Frontend Developer Intern}{Feb 2019 \textbf{--} Aug 2019, Internship}
\resumeItemListStart
\resumeItem{Contributed to the development of modular and reusable \textbf{React.js} components, enhancing scalability and maintainability.}
\resumeItem{Assisted in the deployment of front-end features on \textbf{AWS}, gaining experience in cloud-based solutions.}
\resumeItem{Worked with \textbf{testing frameworks} to identify and resolve issues, ensuring stable and reliable applications.}
\resumeItem{Collaborated with senior developers to implement best practices in front-end development and UI/UX design.}
\resumeItemListEnd

\resumeSubHeadingListEnd
